FoRTE baseline

### 2019-06-05 analysis/paper/paper.Rmd
Add paragraph on ED to introduction

>>>>

A key challenge of vegetation modeling research over the last several decades has been the development of approaches that capture the emergent biogeochemical and ecological outcomes of interactions between individual plants without the need for explicitly simulating each individual [@purves_2008_predictive].
One such approach is the "ecosystem demography" approach, which uses a system of partial differential equations to simulate the emergent mean behavior of "cohorts" of individuals of similar composition, size, and age [@moorcroft_2001_method]. <!-- TODO Run this description by Mike? -->
The original "Ecosystem Demography" (ED) model [@moorcroft_2001_method] was enhanced by @medvigy_2009_mechanistic (as ED2) with fully-coupled leaf physiology, canopy radiative transfer, and micrometeorology, and each of these components have been further refined over the last decade [culminating in ED2.2; @longo_2019_ed1].
Various versions of the ED model have been validated in boreal [@medvigy_2011_predicting], temperate [@medvigy_2009_mechanistic; @dietze_2014_quantitative; @raczka_2018_what], and tropical biomes [@moorcroft_2001_method; @longo_2019_ed2], and have been applied in:
- paleoecological studies [@rollinson_2017_emergent];
- free-air CO~2~ enrichment studies [@dekauwe_2013_forest; @miller_2015_alteration];
- estimation of potential carbon stocks [@hurtt_2004_beyond_potential_vegetation]
